---
title: "homework0"
format: html
editor: visual
execute:
  echo: false
---

## Exercises

(@) Write a Quarto document that defines variables $a=1, b=-1, c=-2$
and print out the solutions to $f(x) = ax^2+bx+c=0$. Do not report complex solutions, only real numbers. 
```{r}
# define the variable
a <- 1
b <- 3
c <- 2

# calculate the solution 
solution1 <- (-b + sqrt(b^2 - 4*a*c)) / (2*a)
solution2 <- (-b - sqrt(b^2 - 4*a*c)) / (2*a)

#| print the results
print(solution1)
print(solution2)
```


(@) Include a graph of $f(x)$ versus $x$ for $x \in (-5,5)$.

This is how you make a plot of a quadratic function:

```{r}
a <- 1 
b <- 3
c <- 2
x <- seq(-5, 5, length = 300)
plot(x, a*x^2 + b*x + c, type = "l")
abline(h = 0, lty = 2)
```

(@) Generate a PDF report using knitr. Do not show the R code, only the solutions and explanations of what the reader is seeing.

(@) Erase the PDF report and reproduce it but this time using $a=1, b=2, c=5$. 

(@) Erase the PDF report and reproduce it but this time using $a=1, b=3, c=2$. 

(@) Create an HTML page with the results for this last set of values, but this time showing the code. 
 

